paper

### 2019-01-11 Report/paper.tex
push my work
push report

    From the pdf parser some of the documents were corrupted with some weird
caracters such as , white space strings

\begin{itemize}
\item
  We use \textbf{\emph{beautiful soup}} and \textbf{\emph{string}}
  libraries to only keep the text that we needed without any special
  character.
\item
  we apply \textbf{\emph{regular expression}} to remove numbers because
  we thought that numbers were not that important.
\item
  We put all the words to lower cases
\item
  We remove the words that were connecting parts of a sentence rather
  than showing subjects, objects or intent. For us these words were not
  that important and were only going to increase the bag of words length
\item
  In some methods we use \textbf{\emph{Lemmatization}} and
  \textbf{\emph{stemming}} and in other methods we don't because we
  wanted to do a mapping with \textbf{\emph{GloVe}} vocabulary which we
  will explain later on.
\end{itemize}

\textbf{\emph{Lemmatization}} is a word variations to the root of the
word (e.g.~working, works, worked changed to work).
\textbf{\emph{Stemming}} is the process of reducing inflected and
derived words to their word stem, base or root form---generally a
written word form As the use of the stop words to reduce the BOW (bag of
words size we also used lemmatization and stemming to be able to reduce
the number of words without taking off any information)

    \textbf{\emph{Lemmatization}} and different form of
\textbf{\emph{Stemming}} were only used with \textbf{\emph{TF-IDF}}
while doing the Keywords extraction, otherwise we prefer keeping the
words as they are because we are doing a mapping with a pretrained
stanford word embedding and we do not want to loose interpretability.

    For the Keywords extraction we use three methods :

The first one whe is a trivial one is to search in the pdf itself for
keywords and extract them, this method is the most accurate but we found
out that for 492 papers we had no keywords included. So we deciced to
use two methods for keywords extraction. The first one is
\textbf{\emph{TF-IDF}} and the second one is \textbf{\emph{Rake}}.

    \begin{itemize}
\tightlist
\item
  \textbf{\emph{TF-IDF}}: Tf--idf is one of the most popular
  term-weighting schemes today, in information retrieval, tf--idf or
  TFIDF, short for term frequency--inverse document frequency, is a
  numerical statistic that is intended to reflect how important a word
  is to a document in a collection or corpus. It is often used as a
  weighting factor in searches of information retrieval, text mining,
  and user modeling. The tf--idf value increases proportionally to the
  number of times a word appears in the document and is offset by the
  number of documents in the corpus that contain the word, which helps
  to adjust for the fact that some words appear more frequently in
  general \cite{Tf-idf}
\end{itemize}

    With TF-IDF we sorted for each document the words with the highest score
and then selected the the 7 first words for each document.

@@

\begin{itemize}
\tightlist
\item
  It splits the text into sentences and generates some words as
  candidates.\\
\item
  Various punctuation signs will be treated as sentence boundaries.
\item
  All words listed in the stopwords file will be treated as phrase
  boundaries. This helps generate candidates that consist of one or more
  non-stopwords. However ,it won't work in cases where the stopword is
  part of the phrase. For example, `new' is listed in RAKE's stopword
  list. This means that neither `New York' nor `New Zealand' can be ever
  a keyword.
\item
  For each keyword candidate generated, the algorithm computes the score
  of the pretended keyword, which is the sum of the scores for each of
  its words (if it's a composed word). The words are scored according to
  their frequency and the typical length of a candidate phrase in which
  they appear.
\item
  The last step is ranking the scores ansd selecting the ones with the
  highest score
\end{itemize}

@@

    Once we have all the keywords from the three methods, we try to select
the most accurate keywords. So we create a method that selects the
intersection of TF-IDF keywords and the Rake keywords with the keywords
of the authors (if there are any keywords in the text), if the
intersection is empty and we have the keywords in the text we only take
the keywords of the text. If we don't have any keywords we take the
intersection of the TF-IDF and the Rake. If again, the intersection is
empty then we only take the TF-IDF keywords because they were closer to
the text keywords than the Rake Keywords.

@@

    Since we don't have the same number of documents for each year we needed
to scale over the years and use the percentage of appearence of a word.
So after groupping the words by year and scaling them we found graph
below \ref{fig1}

@@

With the natural langage processing, we start with a naive method which
consists of clustering the documents using only TF-IDF. Each document
has a vector representation with values for each word present in the
document depending on the frequency of the word in this document
regarding its frequency in all the other documents. So if a word is a
keyword to the document and is not a common word than its value will be
more important than the other words in the vector of the document. Once
we have our vector representation, we select the max features parameter
as 2500, it means that we will only consider the top max\_features
ordered by term frequency across the corpus. On this word representation
we run K-means.

@@

This method does not give good results as we can see it in the graph
below \ref{fig3} all the vectors are together there is no clear
separation between the documents. So we decide to use other methods
using word embeddings and properties of TF-IDF.

@@

\textbf{\emph{GloVe}}, coined from Global Vectors, is a model for
distributed word representation. The model is an unsupervised learning
algorithm for obtaining vector representations for words. Training is
performed on aggregated global word-word co-occurrence statistics from a
corpus (Wikipedia), and the resulting representations showcase
interesting linear substructures of the word vector space. It is
developed as an open-source project at Stanford.\cite{GloVe}

We construct a dictionnary from the words embeddings mapping each word
of a document to its vector representation, than we average all the
vectors of each document. Since each words has its representation in
space, the average of all the words for each document will lead to a
vector representing a document.

Once we get a document vector representation, we apply to it K-means.
The results are better, but we have only two clusters. If we increase
the number of clusters than there is no clear separation anymore
separation. The plot below \ref{fig4} reprensents the documents
belonging to each cluster.

@@

With this method, we did not use the parameter max features of the
TF-IDF vector, we took all the vocabulary generated by all the documents
and we created a method that sorts the document frequency vector, take
the 500 first words and do a weighted average of the words embedding
vectors with the TF-IDF score.

Once we get the weighted average vector, and since we are using a words
embedding of 50 dimentions. We decide to use feature reduction technique
to reduce the number of dimensions and represent our vectors in an other
vector space where all the features are orthogonal to each others.

@@

\textbf{PCA} is a statistical procedure that uses an orthogonal
transformation to convert a set of observations of possibly correlated
variables (entities each of which takes on various numerical values)
into a set of values of linearly uncorrelated variables called principal
components. If there are \textbf{\emph{n}} observations with ****p****
variables, then the number of distinct principal components is
\textbf{\emph{min(n-1,p)}}. This transformation is defined in such a way
that the first principal component has the largest possible variance
(that is, accounts for as much of the variability in the data as
possible), and each succeeding component in turn has the highest
variance possible under the constraint that it is orthogonal to the
preceding components. The resulting vectors (each being a linear
combination of the variables and containing n observations) are an
uncorrelated orthogonal basis set. PCA is sensitive to the relative
scaling of the original variables \cite{PCA}.

Once we get our new vector representation, we apply K-means and we get
the best separation, with a clear separation of 4 clusters as we can see
it in the figure below \ref{fig5}.

@@

For the references graph we choose to construct 4 different graphs to be
able to extract the more information we can. Our first purpose is to be
able to cluster the documents that are about the same subject.

@@

Our first graph is constructed using the references of each document. It
is constructed as follow, for each two documents, if there is an
intersection between the references of both documents then there is a
link. The weights of the edges are the length of the intersection set.
The intuition behind is that the more the weight is high, the more the
documents are likely to be about the same subject since they are citing
the same documents. From this graph, we create a subgraph of it, we
filter the edges keeping only those who have a weight strictly higher
than 3. It means that, each node of the subgraph, is related to at least
one other node with 4 same documents referenced.

@@

The second graph is more about the referenced documents and not about
the documents themselves. The aim of this graph is to see if there are
documents that are more likely to cited together. If it is the case,
then these documents are likely to be about the same subject. It is a
weighted graph constructed as follow: for each document, we create a
link between the references of the document. We create a dictionnary of
links, if the link is already in the dictionnary then we increase the
weight of the link. So for instance, if two references are present
together in the 5 distinct documents, then the weight of the edge would
be of 5. We obtain a graph of 10845 nodes and 148594 edges but we
filtered the edges that have a weight higher than 4 and we get the graph
below represented in this figure \ref{fig6}

@@

\hypertarget{graph-construction}{%
\subsubsection{Graph Construction:}\label{graph-construction}}

First, we built a co-authorship graph based on individual authors. Each
node represented an author, and two nodes were connected if the authors
collaborated on a paper. Other works \cite{cheong2009social},
\cite{hesford2006management} have used a directed graph that only adds a
link from the first author of the paper to all other authors. However,
as we were more interested in collaboration patterns and less in finding
the most influential first author, we built an undirected graph with
edges between all co-authors. On the downside, it yielded a very dense
graph. Hence, we pruned the initial graph by removing nodes that did not
satisfy additional conditions. Intuitively it is clear that a singular
collaboration on a paper does not necessarily indicate that two people
even know each other. A first condition was to link two nodes together
only if the authors corresponding to each node appeared as co-authors in
more than one conference. The graph produced by this approach was much
more sparse and contained much fewer authors. Additionally all connected
components contained fewer than 50 authors, making it possible to
consider each author individually. Such a component is shown in figure
\ref{fig_plot}.

@@

    A second alternative approach was to consider the strength of bounds. In
the graph authors are only linked if they have written at least 2 papers
together. This method yielded a much larger component --containing 441
authors-- as this second condition was weaker. To get an understanding
of author to author relations in this component we needed to further
prune away parts of the graph that are not insightful. When we looked at
individual author within the community, we were interested in
collaborative individuals. Hence we removed nodes that had collaborated
with fewer than 3 connections to other authors. The resulting graph can
be seen in figure \ref{author_collab_large}. Details creating such a
plot can be found in the section dedicated to this below.

@@

    Focusing in on the authors is not the only way to interpret the
co-authorship graph. One should also consider the overall structure of
the graph. As graph is not connected, and contains one large main
component with 1141 authors and 208 very small components with less than
25 authors in them we focused on analyzing the structure of the main
component of the graph. First we aimed to detect sub-communities within
the graph. Modularity is one measure used to find such communities. It
measures the connection strength within a community relative to the
strength of outgoing connections. Networks with high modularity have
dense connections between the nodes within modules but sparse
connections between nodes in different modules. A non-parametric
algorithm for community detection is the Louvain Method
\cite{blondel2008fast}. We used the implementation of Thomas Aynaud
\cite{louvain}. This gives a good partitioning of the graph into 26
communities of median size 42.84. This is quite a large number of
communities, so we considered an alternative way to yield bigger
partitions. An alternate way to find subcommunities is to look at
normalized cuts, which partition the nodes into groups with many
within-group connections and relatively few between-group connections.
The advantage of this method is that we can choose how many cuts to
make, and we are thus able to define the size of subcommunities. Finding
normalized cuts in a graph can be done using \emph{sklearns} spectral
clustering algorithm by passing it the adjacency matrix of the graph.
With this method we are able to neatly separate the main component graph
in three large communities. See figure \ref{normalized}

@@

    \hypertarget{numerical-analysis-of-graphs}{%
\subsubsection{Numerical analysis of
graphs:}\label{numerical-analysis-of-graphs}}

@@

    \hypertarget{plotting-of-co-authorship-graphs}{%
\subsubsection{Plotting of co-authorship
graphs:}\label{plotting-of-co-authorship-graphs}}

Graphs were visualised with the built in plot functions and graph
layouts of networkx. The force directed layout was used as it clusters
together nodes with strong connections. Then the size of each node was
changed based on the position of the node in the graph. Central nodes
with a lot of connections should be larger, while nodes with fewer
connections should be smaller. To achieve this we used the measures of
degree centrality for graphs with few nodes and edges and betweenness
centrality for larger graphs. Degree centrality measures the fraction of
degrees (number of connections) a node has with respect to the total
number of connections in the graph. Betweenness centrality of a node is
the sum of the fraction of all-pairs shortest paths that pass through
it. Degree centrality is more appropriate for smaller graphs as their
structure is still easy to interpret. As by construction betweenness
takes into consideration the degrees of it neighboring nodes, it better
structures the nodes large graphs into central and less central nodes.

@@

We found that participants from 372 institutions participated over the
last 4 years, with a median of 128 institutions per year. The number of
institutions participating increased each year, with a noticeable peak
in 2018, with participants from 261 institutions. This is a considerable
increase from the last conference ICLS in 2016 which had 135
participating institutions. Most participants are from the US, with a
average of 50\% of all participants being from the US. We could also
observe a trend of increase in US participants with only 35\% of US
participants in 2015 and 51\% in 2017, followed by 64\% in 2018.
Overall, participants from 41 nations have participated over the 4
years, with an average of 28 nations represented at each conference.
After the US, participants of Germany, Canada and Singapore make up the
biggest proportion of participants \ref{fig_rep}.

@@

\textbf{International Collaboration:} The U.S. again stands out as a
major player, with most collaborations happening between the U.S. and
other countries. Out of 851 papers, 153 were international
collaborations. Out of these 153, 108 involved at least one U.S.
participant. Excluding U.S. participation we find figure
\ref{figcollab}. We note that some countries, such as Japan, are not
present in this graph. This means that all international collaboration
of these countries, in this case japanese authors, also involves
American authors. Additionally we observed that many asian nations seem
to collaborate almost exclusively with each other or Canada.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_66_0.png}\end{center}
        \caption{Collaborative papers between countries}
        \label{figcollab}
    \end{figure}

@@

    \textbf{Author collaboration}: As the graph yielded by only considering
repeat collaboration during different years is sparse, containing
connected components of size at most 25, we deduce that repeat
collaboration over the years is rather infrequent. As the graph
conditioned on multiple collaboration is more dense (having a component
of the size 400), we deduce that when multiple collaborations with the
same authors happen, they yield work submitted at the same time.

The fact that normalized graph cuts will split the community into three
promted further investigation. As will be discussed in the next section,
the graph of authors that participanted in CSCL yields two large
connected components. By coloring the authors contained in the two CSCL
components different colors, and authors in neither a third color, we
find a similar partitioning of the graph, as can be observed in figure
\ref{CSCL_components}. This is somewhat trivial, as the graph is built
based on collaboration in these conferences. However, the analysis of
nationalities present in the graph yield an interessting results. All
Asian participants from nations other than Singapore are contained in
the same cluster. We also note that one of the CSCL clusters ins closer
to the group of ICLS only participants than the other. Additionaly,
through normaized splits, we find that the section of the normalized cut
containing ICLS only authors is overwhelmingmly american.

@@

Using the data we have of participants over the years, and knowing their
affiliation, we can now find members that change institutions over the
years. Over the years of recording we find 14 participants that have
changed moved countries and 47 that have moved institutions. We can see
that most movement occured within the US respectively Europe,
\ref{fig_move}.

@@

The distribution of referenced publications years are plotted in the
graph \ref{count_ref_docs}. We can see from the graph that there is a
kind of a trend, each two, three years there is a pick of documents
referenced followed by a two or three years of stagnancy. We can also
notice that throughouts the year each pick is higher than the older one,
which can be explained by the fact that The International Society of the
Learning Sciences community is investigating more and more tools to
facilitate learning over the years.

@@

    Since the number of documents is increasing over the years, we also
wanted to investigate more if the relevance of all the documents
published is increasing too. Using Pagerank algorithm and the In-degree
of each nodes to get the most influancial documents referenced of the
citation graph that we constructed (graph3) before. We filtered the
first 100 documents and then contructed a histogram of the counts. We
obtain the figure \ref{fig7}:

@@

    We can see that in the top 100 cited documents more than 12\% are from
2006, 8\% are from 2013, 6\% from 2014\ldots{} We can not say that we
have the same trend as before, and the relevance of the documents is
increasing in the same way than with the number of publications but what
we can say is that more than 50\% of the most cited documents are from
2006 until 2016, we is 10 years. The other half is between 1977 until
2005 which represents more than 25 years. On top of that, 2016 is the
most important year in term of publications and maybe some documents did
not have enough time to be cited yet.

@@

    We also noticed from the first graph that some documents were more
likely to cited together. We can say that the more two documents are
likely to cited together the more it is probable that both documents are
about the same subject From the table \ref{fig8} we can also notice that
some papers cites like to cite the same authors together, which is logic
in a sense, because if some authors always treat about the same subjects
then they are experts in that field and a lot of their publications are
relevant and can be cited together.

@@

    Using this graph, we also want to extract if there are some clusters of
papers cited together. As we explained before, we run strongly connected
algorithm to check if some cited documents are more likely to be cited
together, and this will give us clusters of cited documents that are
more likely to be about the same subjects. We can visualise one cluster,
the most important one.

>>>>

    From the pdf parser some of the documents were corrupted with some weird
characters such as , white space strings

\begin{itemize}
\item
  We used \textbf{\emph{beautiful soup}} and \textbf{\emph{string}}
  libraries to only keep the text that we needed without any special
  character.
\item
  we applied \textbf{\emph{regular expression}} to remove numbers
  because we thought that numbers were not that important.
\item
  We put all the words to lower cases
\item
  We removed the words that were connecting parts of a sentence rather
  than showing subjects, objects or intent (\textbf{\emph{stopwords}}).
  For us these words were not that important and were only going to
  increase the bag of words length
\item
  In some methods we use \textbf{\emph{Lemmatization}} and
  \textbf{\emph{stemming}} and in other methods we don't because we
  wanted to do a mapping with \textbf{\emph{GloVe}} vocabulary which we
  will explain later on.
\end{itemize}

\textbf{\emph{Lemmatization}} is a word variations to the root of the
word (e.g.~working, works, worked changed to work).
\textbf{\emph{Stemming}} is the process of reducing inflected and
derived words to their word stem, base or root form---generally a
written word form.

As the use of the stop words to reduce the BOW (bag of words size) we
also used lemmatization and stemming to be able to reduce the number of
words without taking off any valuable information.

    \textbf{\emph{Lemmatization}} and different form of
\textbf{\emph{Stemming}} were only used with \textbf{\emph{TF-IDF}}
while doing the Keywords extraction, otherwise we prefered keeping the
words as they were because we were doing a mapping with a pretrained
stanford word embedding and sometimes root forms were not in the
dictionnary of words of the pre-trained words-vectors.

    For the Keywords extraction we used three methods :

The first one is a trivial one is to search in the pdf itself for
keywords and extract them, this method is the most accurate but we found
out that for 492 papers we had no keywords included. So we deciced to
use two methods for keywords extraction. The first one is
\textbf{\emph{TF-IDF}} and the second one is \textbf{\emph{Rake}}.

    \begin{itemize}
\tightlist
\item
  \textbf{\emph{TF-IDF}}: Tf--idf is one of the most popular
  term-weighting schemes today, in information retrieval, tf--idf or
  TFIDF, short for term frequency--inverse document frequency, is a
  numerical statistic that is intended to reflect how important a word
  is to a document in a collection or corpus. It is often used as a
  weighting factor in searches of information retrieval, text mining,
  and user modeling. The tf--idf value increases proportionally to the
  number of times a word appears in the document and is offset by the
  number of documents in the corpus that contain the word, which helps
  to adjust for the fact that some words appear more frequently in
  general \cite{Tf-idf}.
\end{itemize}

    With TF-IDF we sorted for each document the words with the highest score
and then selected the the 7 first words of each document.

@@

\begin{itemize}
\tightlist
\item
  It splits the text into sentences and generates some words as
  candidates.\\
\item
  Various punctuation signs will be treated as sentence boundaries.
\item
  All words listed in the stopwords file will be treated as phrase
  boundaries. This helps generate candidates that consist of one or more
  non-stopwords. However, it won't work in cases where the stopword is
  part of the phrase. For example, `new' is listed in RAKE's stopword
  list. This means that neither `New York' nor `New Zealand' can be ever
  a keyword.
\item
  For each keyword candidate generated, the algorithm computes the score
  of the pretended keyword, which is the sum of the scores for each of
  its words (if it's a composed word). The words are scored according to
  their frequency and the typical length of a candidate phrase in which
  they appear.
\item
  The last step is ranking the scores and selecting the ones with the
  highest score
\end{itemize}

@@

    Once we have all the keywords from the three methods, we try to select
the most accurate keywords. So we created a method that selects the
intersection of TF-IDF keywords and the Rake keywords with the keywords
of the authors (if there are any keywords in the text), if the
intersection is empty and we have the keywords in the text we only take
the keywords of the text. If the paper does not have keywords, we take
the intersection of the TF-IDF and the Rake. If again, the intersection
is empty then we only take the TF-IDF keywords because they were closer
to the text keywords than the Rake Keywords.

@@

    Since we don't have the same number of documents for each year we needed
to scale over the years and use the percentage of appearence of a word.
So after groupping the words by year and scaling them we found the graph
below \ref{fig1}.

@@

With the natural langage processing, we started with a naive method
which consists of clustering the documents using only TF-IDF. Each
document has a vector representation with values for each word present
in the document depending on the frequency of the word in this document
regarding its frequency in all the other documents. So if a word is a
keyword to the document and is not a common word than its value will be
more important than the other words in the vector of the document. Once
we obtained our vector representation, we selected the max features
parameter as 2500, it means that we only considered the top
max\_features ordered by term frequency across the corpus. On this word
representation we run K-means.

@@

This method did not give good results as we can see it in the graph
below \ref{fig3}. All the vectors are together there is no clear
separation between the documents. So we decide to use other methods
using words embeddings and properties of TF-IDF.

@@

\textbf{\emph{GloVe}}, coined from Global Vectors, is a model for
distributed word representation. The model is an unsupervised learning
algorithm for obtaining vector representations for words. Training is
performed on aggregated global word-word co-occurrence statistics from a
corpus (Wikipedia), and the resulting representations showcase
interesting linear substructures of the word vector space. It is
developed as an open-source project at Stanford.\cite{GloVe} The goal of
GloVe is to group words with similar meaning together in a new vector
space.

We constructed a dictionnary from the words embeddings mapping each word
of a document to its vector representation, than we averaged all the
vectors of each document. Since each words has its representation in
space, the average of all the words for each document will lead to a
vector representing a document.

Once we obtained a document vector representation, we applied to it
K-means. The results were slightly better, but we had only two clear
separate clusters. If we increase the number of clusters than there is
no clear separation anymore. The plot below \ref{fig4} reprensents the
documents belonging to each cluster.

@@

With this method, we did not use the parameter max features of the
TF-IDF vector, we took all the vocabulary generated by all the documents
and we created a method that sorts the document frequency vector. We
selected the 500 first words and did a weighted average of the words
embedding vectors with the TF-IDF score.

Once we get the weighted average vector, and since we were using a words
embedding of 50 dimentions. We decided to use feature reduction
technique to reduce the number of dimensions and represent our vectors
in an other vector space where all the features are orthogonal to each
others.

@@

\textbf{PCA} is a statistical procedure that uses an orthogonal
transformation to convert a set of observations of possibly correlated
variables (entities each of which takes on various numerical values)
into a set of values of linearly uncorrelated variables called principal
components. If there are \textbf{\emph{n}} observations with
\textbf{\emph{p}} variables, then the number of distinct principal
components is \textbf{\emph{min(n-1,p)}}. This transformation is defined
in such a way that the first principal component has the largest
possible variance (that is, accounts for as much of the variability in
the data as possible), and each succeeding component in turn has the
highest variance possible under the constraint that it is orthogonal to
the preceding components. The resulting vectors (each being a linear
combination of the variables and containing n observations) are an
uncorrelated orthogonal basis set. \cite{PCA}.

Once we get our new vector representation, we applied K-means and we
obtained the best separation, with a clear separation of 4 clusters as
we can see it in the figure below \ref{fig5}.

@@

For the references graph we chose to construct 4 different graphs to be
able to extract the more information we can. Our first purpose is to be
able to cluster the documents that are about the same subject and to
gain more insights about the most influencial papers, trends of
citations\ldots{}

@@

Our first graph is constructed using the references of each document. It
is constructed as follows, for each two documents, if there is an
intersection between the references of both documents then there is a
link. The weights of the edges are the length of the intersection set.
The intuition behind it, is that the more the weight is high, the more
the documents are likely to be about the same subject since they are
citing the same documents. From this graph, we create a subgraph of it,
we filter the edges keeping only those who have a weight strictly higher
than 3. It means that, each node of the subgraph, is related to at least
one other node with 4 same documents referenced.

@@

The second graph is more about the referenced documents and not about
the documents themselves. The aim of this graph is to see if there are
documents that are more likely to cited together. If it is the case,
then these documents are likely to be about the same subject. It is a
weighted graph constructed as follow: for each document, we create a
link between the references of the document. We create a dictionnary of
links, for each new document, if two references of this latter have
already a link in the dictionnary then we increase the weight of the
link.

So for instance, if two references are present together in the 5
distinct documents, then the weight of the edge would be of 5. We obtain
a graph of 10845 nodes and 148594 edges but we filtered the edges that
have a weight higher than 4 and we get the graph below represented in
this figure \ref{fig6}

@@

\hypertarget{graph-construction}{%
\subsubsection{Graph Construction}\label{graph-construction}}

First, we built a co-authorship graph based on individual authors. Each
node represented an author, and two nodes were connected if the authors
collaborated on a paper. Other works \cite{cheong2009social},
\cite{hesford2006management} have used a directed graph that only adds a
link from the first author of the paper to all other authors. However,
as we were more interested in collaboration patterns and less in finding
the most influential first author, we built an undirected graph with
edges between all co-authors. On the downside, it yielded a very dense
graph. Hence, we pruned the initial graph by removing nodes that did not
satisfy additional conditions. Intuitively it is clear that a singular
collaboration on a paper does not necessarily indicate that two people
even know each other. A first condition was to link two nodes together
only if the authors corresponding to each node appeared as co-authors in
more than one conference. The graph produced by this approach was much
more sparse and contained much fewer authors. Additionally all connected
components contained fewer than 35 authors, making it possible to
consider each author individually. Such a component is shown in figure
\ref{fig_plot}.

@@

    A second alternative approach was to consider the strength of bounds. In
this graph authors are only linked if they have written at least 2
papers together. This method yielded a much larger component
--containing 441 authors-- as this second condition was weaker. To get
an understanding of author to author relations in this component we
needed to further prune away parts of the graph that are not insightful.
When we looked at individual author within the community, we were
interested in collaborative individuals. Hence we removed nodes that had
fewer than 3 connections to other nodes. The resulting graph can be seen
in figure \ref{author_collab_large}. Details creating such a plot can be
found in the section dedicated to this below.

@@

    Focusing in on the authors is not the only way to interpret the
co-authorship graph. One should also consider the overall structure of
the graph. As the co-authorship graph is not connected, and contains one
large main component with 1141 authors and 208 very small components
with less than 25 authors in them we focused on analyzing the structure
of the main component of the graph. First we aimed to detect
sub-communities within the graph. Modularity is one measure used to find
such communities. It measures the connection strength within a community
relative to the strength of outgoing connections. Networks with high
modularity have dense connections between the nodes within the
subcommunites but sparse connections between nodes in different
subcommunites. A non-parametric algorithm for community detection is the
Louvain Method \cite{blondel2008fast}. We used the implementation of
Thomas Aynaud \cite{louvain}. This gives a good partitioning of the
graph into 26 communities of median size 42.84. This is quite a large
number of communities, so we considered an alternative way to yield
bigger partitions. For this we looked at normalized cuts, which
partition the nodes into groups with many within-group connections and
relatively few between-group connections. The advantage of this method
is that we can choose how many cuts to make, and we are thus able to
define the size of subcommunities. Finding normalized cuts in a graph
can be done using \emph{sklearns} spectral clustering algorithm by
passing it the adjacency matrix of the graph. With this method we are
able to neatly separate the main component graph in three large
communities, as can be seen in figure \ref{normalized}

@@

    \hypertarget{numerical-analysis-of-graphs}{%
\subsubsection{Numerical analysis of
graphs}\label{numerical-analysis-of-graphs}}

@@

    \hypertarget{plotting-of-co-authorship-graphs}{%
\subsubsection{Plotting of co-authorship
graphs}\label{plotting-of-co-authorship-graphs}}

Graphs were visualised with the built in plot functions and graph
layouts of networkx. The force directed layout was used as it clusters
together nodes with strong connections. As this layout is produced by
iterations and based on random initial conditions, we set a fix random
seed to be able to reproduce the positioning. The size of each node was
changed based on the position of the node in the graph. Central nodes
with a lot of connections should be larger, while nodes with fewer
connections should be smaller. To achieve this we used the measures of
degree centrality for graphs with few nodes and edges and betweenness
centrality for larger graphs. Degree centrality measures the fraction of
degrees (number of connections) a node has with respect to the total
number of connections in the graph. Betweenness centrality of a node is
the sum of the fraction of all-pairs shortest paths that pass through it
\ref{borgatti2014social}. We found that degree centrality is more
appropriate for smaller graphs as their structure is still easy to
interpret. As by construction betweenness takes into consideration the
degrees of it neighboring nodes, it better structures the nodes large
graphs into central and less central nodes.

@@

Participants from 372 institutions participated over the last 4 years,
with a median of 128 institutions per year. The number of institutions
participating increased each year, with a noticeable peak in 2018, with
participants from 261 institutions. This is a considerable increase from
the last conference ICLS in 2016 which had 135 participating
institutions. Most participants are from the US, with a average of 50\%
of all participants being from the US. We could also observe a trend of
increase in US participants with only 35\% of US participants in 2015
and 51\% in 2017, followed by 64\% in 2018. Overall, participants from
41 nations have participated over the 4 years, with an average of 28
nations represented at each conference. After the US, participants of
Germany, Canada and Singapore make up the biggest proportion of
participants \ref{figrep}.

@@

\textbf{International Collaboration:} The U.S. again stands out as a
major player, with most collaborations happening between the U.S. and
other countries. Out of 851 papers, 153 were international
collaborations. Out of these 153, 108 involved at least one U.S.
participant. Excluding US participation we find the collaboration graph
presented in figure \ref{figcollab}. We note that some countries, such
as Japan, are not present in this graph. This means that all
international collaboration of these countries, in this case japanese
authors, also involves American authors. Additionally we observed that
many Asian nations seem to collaborate almost exclusively with each
other or Canada.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_66_0.png}\end{center}
        \caption{Collaborative papers between countries excluding US}
        \label{figcollab}
    \end{figure}

@@

    \textbf{Author collaboration}: As the graph yielded by only considering
repeat collaboration during different years is sparse, containing
connected components of size at most 31, we deduce that repeat
collaboration over the years is rather infrequent. As the graph
conditioned on multiple collaboration is more dense (having a connected
component with more than 400 authors), we deduce that when multiple
collaborations with the same authors happen, they yield work submitted
at the same time.

The fact that normalized graph cuts will split the community into three
promted further investigation. As will be discussed in the next section,
the graph of authors that participanted in CSCL yields two large
connected components. By coloring the authors contained in the two CSCL
components different colors, and authors in neither a third color, we
find a similar partitioning of the graph, as can be observed in figure
\ref{CSCL_components}. This is somewhat trivial, as the graph is built
based on collaboration in these conferences. However, the analysis of
nationalities present in the graph yielded an interessting results. All
Asian participants from nations other than Singapore are contained in
the same cluster. We also note that one of the CSCL clusters ins closer
to the group of ICLS only participants than the other. Additionaly,
through normaized splits, we find that the section of the normalized cut
containing ICLS only authors is overwhelmingmly american.

@@

Using the data we have of participants over the years, and knowing their
affiliation, we can now find members that change institutions over the
years. Over the years of recording we find 14 participants that have
changed moved countries and 47 that have moved institutions. We can see
that most movement occured within the US respectively Europe, see figure
\ref{fig_move}.

@@

The distribution of referenced publications years are plotted in the
graph \ref{count_ref_docs}. We can see from the graph that there is a
kind of a trend, each two, three years there is a pick of documents
referenced followed by a two or three years of stagnancy. We can also
notice that throughouts the year each pick is higher than the older one,
which can be explained by the fact that The International Society of the
Learning Sciences community is investigating more and more tools to
facilitate the learning over the years.

@@

    Since the number of documents is increasing over the years, we also
wanted to investigate more if the relevance of all the documents
published is increasing too. Using Pagerank algorithm and the In-degree
of each nodes to get the most influancial documents referenced of the
citation graph that we constructed (graph3) before. We filtered the
first 100 documents and then contructed a histogram of the counts by
year. We obtain the figure \ref{fig7}:

@@

    We can see that in the top 100 cited documents more than 12\% are from
2006, 8\% are from 2013, 6\% from 2014\ldots{} We can not say that we
have the same trend as before, and the relevance of the documents is
increasing in the same way than with the number of publications but what
we can say is that more than 50\% of the most cited documents are from
2006 until 2016, which is 10 years. The other half is between 1977 until
2005 which represents more than 25 years. On top of that, 2016 is the
most important year in term of publications and maybe some documents did
not have enough time to be cited yet.

@@

    We also noticed from the first graph that some documents were more
likely to cited together. We can say that the more two documents are
likely to cited together the more it is probable that both documents are
about the same subject From the table \ref{fig8} we can also notice that
some papers are more likely to cite distinct publications of the same
author, which is logic in a sense, because if some authors always treat
about the same subject then they are experts in that field and a lot of
their publications are relevant and can be cited together.

@@

    Using this graph, we also want to extract if there are some clusters of
papers cited together. As we explained before, we run strongly connected
algorithm to check if some cited documents are more likely to be cited
together, and this will give us clusters of cited documents that are
more likely to be about the same subjects. We can visualise one cluster,
the most important one in figure \ref{fig12}.
